Current State of Knowledge Representation Systems for Robotics

### 2011-11-23 krs-survey.tex
Reformatted the intro to remoze itemization

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}

@@

The idea of \emph{Cognitive robotics} was coined in the early 1990s by Reiter.
In a chapter on that subject in \emph{Fondations of Artifical
Intelligence}~\cite{Levesque2007}, Levesque reminds about the manifesto they
wrote together in 1998:

@@

This survey focuses on the knowledge issue: we aims at establishing the current
landscape of approaches to the knowledge representation problem in the research
community.

We have identified over ten projects that are designed for explicit knowledge
manipulation within a robot. By knowledge manipulation, we mainly mean:

	\item symbolic representation of assertions, be it static statements on the
	world or spatio-temporal events,

	\item reasoning that this representation enables,

We will also try, for each project, to make clear

	\item how new facts can be acquired, \ie how informations from perception
	or interaction are turned into knowledge,

	\item how, in return, symbolic concept are \emph{anchored} into the robot
	sensori-motor space,

	\item how the knowledge representation system integrates with the
	decisional layers of the robot, and if this leads to better robotic
	control.

>>>>

\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{supertabular}
\usepackage{pdflscape} %% Used for very big table
\usepackage{moreverb}
\usepackage[table]{xcolor}
\usepackage{listings}
\usepackage{paralist}
\usepackage{fancyhdr}
\usepackage[draft]{fixme}

@@

The idea of \emph{Cognitive Robotics} was coined in the early 1990s by Reiter.
In a chapter on that subject in \emph{Fondations of Artifical
Intelligence}~\cite{Levesque2007}, Levesque reminds about the manifesto they
wrote together in 1998:

@@

This survey focuses on the knowledge issue: we aims at establishing the current
landscape of approaches to the knowledge representation problem in the research
community, at summarizing the major trends and identifying the possible
shortcomings.

We have identified over ten projects that either are explicitely advertised as
knowledge representation systems or involve explicit knowledge manipulation
within a robot. By knowledge manipulation, we mean symbolic representation of
assertions, be it static statements on the world or spatio-temporal events, and
reasoning on this representation.

We also try, for each project, to make clear \begin{inparaenum} \item how new
facts can be acquired, \ie how informations from perception or interaction are
turned into knowledge, \item how, in return, symbolic concept are
\emph{anchored} into the robot sensori-motor space, \item how the knowledge
representation system integrates with the decisional layers of the robot, and
how this leads to better robotic control.\end{inparaenum}
